---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Onnolyzer

<!-- badges: start -->
[![R-CMD-check](https://github.com/kacebron/Onnolyzer/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/kacebron/Onnolyzer/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of Onnolyzer is to aid users of LIFT device mounted ton LIFT to process raw .csv files to derive photosynthetic and statistical parameters (based on Beat Keller and Nicolas Zendonadi)'s published data below:

Keller, B., Vass, I., Matsubara, S., Paul, K., Jedmowski, C., Pieruschka, R., ... & Muller, O. (2019). Maximum fluorescence and electron transport kinetics determined by light-induced fluorescence transients (LIFT) for photosynthesis phenotyping. Photosynthesis Research, 140(2), 221-233.

Zendonadi dos Santos, N., Piepho, H. P., Condorelli, G. E., Licieri Groli, E., Newcomb, M., Ward, R., ... & Muller, O. (2021). High‐throughput field phenotyping reveals genetic variation in photosynthetic traits in durum wheat under drought. Plant, cell & environment, 44(9), 2858-2878.

## Installation

You can install the development version of Onnolyzer like so:

``` r
devtools::install_github("kacebron/Onnolyzer")
```

## Example

This is a sample workflow first to correct the date and time (In case you forgot to change / adjust the date and time in LIFT computer before you start your measurement)

```{r example}
library(Onnolyzer)
## basic example code

# Filename
data_file_dt <- get_file_datetime("012007~~2025_08_25__13_04_02_436_data.csv", "CET")
fit_file_dt <- get_file_datetime("012007~~2025_08_25__13_04_02_436_fit", "CET")
spectra_file_dt <- get_file_datetime("003004~~2025_08_25__12_09_19_859_spectr", "CET")

# Filepath
data_file_path <- '/Users/kelvinacebron/Documents/1_IBG2/2_Materials/LIFT_ANALYSIS/Sample_data/TimeCorrectionNeeded/012007~~2025_08_25__13_04_02_436_data.csv'
fit_file_path <- '/Users/kelvinacebron/Documents/1_IBG2/2_Materials/LIFT_ANALYSIS/Sample_data/TimeCorrectionNeeded/012007~~2025_08_25__13_04_02_436_fit.csv'
spectra_file_path <- '/Users/kelvinacebron/Documents/1_IBG2/2_Materials/LIFT_ANALYSIS/Sample_data/TimeCorrectionNeeded/003004~~2025_08_25__12_09_19_859_spectr.csv'

# Set time threshold for minimum difference needed between filename and content
time_threshold <- 5 * 60

# Define time discrepancy
computer_time <- as.POSIXct("2025-08-21 15:48:00", tz = "CET")
actual_time   <- as.POSIXct("2025-08-25 12:36:00", tz = "CET")

# Offset difference
time_offset <- difftime(actual_time, computer_time, units = "secs")

newdf <- adjust_dt_datacsv(data_file_path, data_file_dt, time_threshold, time_offset)
newdf <- adjust_dt_fitcsv(fit_file_path, fit_file_dt, time_threshold, time_offset)
newdf <- adjust_dt_spectra(spectra_file_path, spectra_file_dt, time_threshold, time_offset)

# This is a more robust code if you want to change all your files in the folder (works only on a single date)
folder_path <- "/Users/kelvinacebron/Documents/1_IBG2/2_Materials/LIFT_ANALYSIS/Sample_data/TimeCorrectionNeeded"

# --- Loop through all CSV files in folder ---
files <- list.files(folder_path, pattern = "\\.csv$", full.names = TRUE)

for (f in files) {
  adjust_dt_by_filetype(f, time_threshold, time_offset)
}


```

This is a sample workflow to derive photosynthetic and statistical parameters 
```{r}
# Set Settings
settings <- lift_settings()

# Load Raw LIFT files
fnames <- list.files("/Users/kelvinacebron/Documents/1_IBG2/2_Materials/LIFT_ANALYSIS/Sample_data/TimeCorrectionNeeded", pattern = "_data.csv")

my_raw <- lift_load_raw(
   fpath = "/Users/kelvinacebron/Documents/1_IBG2/2_Materials/LIFT_ANALYSIS/Sample_data/TimeCorrectionNeeded",
   fnames = fnames,
   f = 427,
   sep = ","
 )

# Parse raw data
clean <- lift_parse_metadata(my_raw, f = 427)

# Calculate Fq.Fm, Fr's and regression fitting
data_fit <- redox_fit(clean, f = 427, method = c("absolute", "relative"), regression = TRUE)

write.csv(data_fit, "/Users/kelvinacebron/Documents/1_IBG2/2_Materials/LIFT_ANALYSIS/Sample_output/sample_output_package.csv")

# End
```

